Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-21 review_article.Rmd

@@

>>>>

(insert figure of both types of interactivity)

Additionally, interactivity allows the user to toggle between different variables, map views or multiple realizations of possible future scenarios [@goodchild1994introduction]. Thus providing additional mechanisms for the users comprehension as well as the uncertainty of the available information (@maceachren1992visualizing; @van1994visualization).

These interactive features provide an opportunity for users to explore the additional information available. This helps users to understand and interpret the spatial distribution presented, as well as validate, explain or explore the presented statistics and their relationships to each other and/or their underlying spatial distribution. This allows relationships between spatial areas and diseases to be explored with sophistication in non-traditional but still 'cognitively accesible' ways [@TNTEA]. The interactive features of the publically available maps identified by @roberts2019communication allow the exploration of geographic hierarchies, population distribution, statistical uncertainty, demographics and socio-economic indicators.
@TNTEA suggested LM plots as a solution to linking cartography and statistical graphics.

(insert figures showing different interactivity)

@@

## Micromaps
XXX Something needs to be said about micromaps https://cran.r-project.org/web/packages/micromapST/vignettes/JSSmicromapSTv63i03.pdf
